
## Peak shaving 

::: {.absolute top="0" left="100%"}
::: {.sectionhead}
[Objectives]{style="opacity:0.15"} </br> 
[Agenda]{style="opacity:0.15"} </br> 
[Background]{style="opacity:0.15"} </br> 
[Examples]{style="opacity:0.15"} </br> 
[Paper 5 / 5]{style="opacity:0.75"} </br> 
[Conclusion]{style="opacity:0.15"}  
:::
:::

::: {.absolute top="15%" left="0%"}
<!-- Showing only the peaks -->
```{r}
#| echo: false
#| fig-height: 4
#| fig-width: 5.5
library(tidyverse)
load("data/ecm_data_TVB_pred.Rdata")
peak_shave <- ecm_data_TVB_pred %>% dplyr::filter(start_date >= '2021-04-14 00:00:00' & start_date <= '2021-04-14 23:00:00') 


ggplot(data = peak_shave) +
  geom_line(aes(x = start_date, y = kwh), color = "blue") +
  theme_minimal() +
  labs(
    y = "Loads (kW)",
    x = "Date",
    title = "Example: shaving the peaks"
  ) +
  annotate("text", x= as.POSIXct("2021-04-14 06:00:00"), y = 43, label = "Peak") +
  annotate("text", x= as.POSIXct("2021-04-14 09:00:00"), y = 46, label = "Peak") +
  annotate("text", x= as.POSIXct("2021-04-14 18:00:00"), y = 44, label = "Peak") 
```
:::


::: {.absolute top="25%" left="52%"}
::: {style="font-size: 0.55em"}
::: {.incremental}
- The grid owner wants to reduce the **peaks** to stabilize the grid
- Thus, tariffs for large loads are more expensive
- Objective of paper was to improve the economics of solar panels and batteries with load forecasting 
- Building with annual consumption 2900 MWh, 891 kW max peak
:::
:::
:::



## Peak shaving 

::: {.absolute top="0" left="100%"}
::: {.sectionhead}
[Objectives]{style="opacity:0.15"} </br> 
[Agenda]{style="opacity:0.15"} </br> 
[Background]{style="opacity:0.15"} </br> 
[Examples]{style="opacity:0.15"} </br> 
[Paper 5 / 5]{style="opacity:0.75"} </br> 
[Conclusion]{style="opacity:0.15"}  
:::
:::



::: {.absolute top="15%" left="0%"}
<!-- Forecast based peak shaving  -->
```{r}
#| echo: false
#| fig-height: 4
#| fig-width: 5.5
load("data/ecm_data_TVB_pred.Rdata")
peak_shave <- ecm_data_TVB_pred %>% dplyr::filter(start_date >= '2021-04-14 00:00:00' & start_date <= '2021-04-14 23:00:00') 


ggplot(data = peak_shave) +
  geom_line(aes(x = start_date, y = kwh), color = "blue") +
  theme_minimal() +
  labs(
    y = "Loads (kW)",
    x = "Date",
    title = "Example: shaving the peaks"
  ) +
  annotate("text", x= as.POSIXct("2021-04-14 06:00:00"), y = 43, label = "Peak") +
  annotate("text", x= as.POSIXct("2021-04-14 09:00:00"), y = 46, label = "Peak") +
  annotate("text", x= as.POSIXct("2021-04-14 18:00:00"), y = 44, label = "Peak") +
  annotate("text", x= as.POSIXct("2021-04-14 08:00:00"), y = 40, label = "Forecast", color="steelblue") +
  annotate("text", x= as.POSIXct("2021-04-14 18:20:00"), y = 40, label = "Forecast", color="steelblue") +
  geom_segment(aes(x = as.POSIXct("2021-04-14 05:00:00"), y =41, xend=as.POSIXct("2021-04-14 11:00:00"), yend=41), color="steelblue", linetype = 2) +
  geom_segment(aes(x = as.POSIXct("2021-04-14 16:30:00"), y =41, xend=as.POSIXct("2021-04-14 20:00:00"), yend=41), color="steelblue", linetype = 2) 
```
:::

::: {.absolute top="25%" left="52%"}
::: {style="font-size: 0.55em"}
::: {.incremental}
- Battery storage was only economically beneficial when forecasting was deployed
- Most of the savings came from **peak shaving**, not from increased self-consumption
:::
:::
:::


::: {.fragment .fade-in}
::: {.absolute top="75%" left="0%"}
::: {.callout-note icon=false appearance="minimal"}
::: {style="font-size: 0.55em"}
Fagerström, Jonathan, Kari Aamodt Espegren, Josefine Selj, and Alexander Severinsen. 2019. “Forecasting and Technoeconomic Optimization of PV-Battery Systems for Commercial Buildings.” In ECEEE Summer Study Proceedings, 949–54, <https://www.eceee.org/library/conference_proceedings/eceee_Summer_Studies/2019/5-smart-and-sustainable-communities/forecasting-and-technoeconomic-optimization-of-pv-battery-systems-for-commercial-buildings/>
:::
:::
:::
:::

<!--
## Peak shaving 


::: {.absolute top="0" left="100%"}
::: {.sectionhead}
[Objectives]{style="opacity:0.15"} </br> 
[Agenda]{style="opacity:0.15"} </br> 
[Background]{style="opacity:0.15"} </br> 
[Examples]{style="opacity:0.15"} </br> 
[Paper 5 / 5]{style="opacity:0.75"} </br> 
[Conclusion]{style="opacity:0.15"}  
:::
:::

::: {.absolute top="15%" left="0%"}
```{r}
#| echo: false
#| fig-height: 4
#| fig-width: 5.5
Month <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")
Case_c <- c(12,9,11,6,15,27,18,22,24,32,26,17)
Case_d <- c(5,0,0,0,9,10,8,8,15,8,11,0) 

df <- tibble(Month,Case_c,Case_d)

df$Month <- factor(df$Month, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))



df %>%
  ggplot(aes(x=Month, group=1)) +
  geom_line(aes(y=Case_d),color="black") +
  geom_line(aes(y=Case_c), color="steelblue", linetype="dashed") +
  theme_minimal() +
  labs(
    x = "",
    y="% peak shaving",
    title="Monthly results - Peak shaving (%) ") +
  annotate("text", x= "Oct", y = 33, label = "32%")

```
:::

-->











