---
format: 
  revealjs:
    theme: ["../fonts_aneo.scss"]
    css: ../styles.css
from: markdown+emoji
---

## Documentation of energy savings


::: {.absolute top="0" left="100%"}
::: {.sectionhead}
[Objectives]{style="opacity:0.15"} </br> 
[Agenda]{style="opacity:0.15"} </br> 
[Background]{style="opacity:0.15"} </br> 
[Examples]{style="opacity:0.75"} </br> 
[Paper 1 / 5]{style="opacity:0.15"} </br> 
[Conclusion]{style="opacity:0.15"}  
:::
:::


::: {.absolute top="%" left="0"}
::: {style="text-align: center"}


<!-- Before you get the results from the retrofitting -->
```{r, fig.width=4.5,fig.height=6}
library(tidyverse)
options(scipen=999)
status <- c("Before retrofitting \n (2018)", "After retrofitting \n (2021)")
kwh <- c(800000, 0)
df <- tibble(status,kwh)

status_before <- "Before retrofitting"
kwh_before <- 800000
df_before <- tibble(status_before,kwh_before)

ggplot(df, aes(x = reorder(status, -kwh), y = kwh)) +
  geom_col(width = 0.6, 
           fill="steelblue",
           position = position_dodge(0.1)) +
  theme_minimal() +
  geom_text(aes(label=format(kwh, big.mark = " ", scientific = FALSE)), vjust=1.6, color="white", size=4) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=16)) +
  xlab("") +
  ylab("Yearly energy consumption (kWh)") + 
  scale_y_continuous(labels=function(x) format(x, big.mark = " ", scientific = FALSE))

```

:::
:::


::: {.absolute top="27%" left="30%"}
::: {style="color: #619CFF; font-size: 3em"}

? 

:::
:::



::: {.absolute top="20%" left="50%"}
::: {style="font-size: 0.7em"}



::: {.fragment .fade-in-then-out}
Example 

- Retrofitting of a grocery store in 2020 
- Ventilation and cooling system are upgraded. New LED-lights
- You guarantee the customer a 50% reduction of energy use
:::

:::
:::


::: {.absolute top="30%" left="50%"}
::: {style="font-size: 0.7em"}

::: {.fragment .fade-in-then-out}

A year after the retrofitting the results are finally available...

:::


:::
:::




. . .

::: {.absolute top="%" left="0"}
::: {style="text-align: center"}

<!-- After you get the results -->
```{r, fig.width=4.5,fig.height=6}
options(scipen=999)
# ---- make data from Enova ----
status <- c("Before retrofitting \n (2018)", "After retrofitting \n (2021)")
kwh <- c(800000, 400000)
df <- tibble(status,kwh)

status_before <- "Before retrofitting"
kwh_before <- 800000
df_before <- tibble(status_before,kwh_before)

ggplot(df, aes(x = reorder(status, -kwh), y = kwh)) +
  geom_col(width = 0.6, 
           fill="steelblue",
           position = position_dodge(0.1)) +
  theme_minimal() +
  geom_text(aes(label=format(kwh, big.mark = " ", scientific = FALSE)), vjust=1.6, color="white", size=4) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=16)) +
  xlab("") +
  ylab("Yearly energy consumption (kWh)") + 
  scale_y_continuous(labels=function(x) format(x, big.mark = " ", scientific = FALSE))

```

:::
:::


::: {.absolute top="20%" left="50%"}
::: {style="font-size: 0.7em"}

::: {.incremental}

- Great! A 50% reduction :sunglasses:
- Customer argue that the result was because of the mild winter in 2021!
- You correct for the temperature differences^1^

:::

:::
:::

::: {.absolute top="100%" left="5%"}
::: {style="font-size: 0.5em"}

::: {.fragment .fade-in}
1. More information about adjusting for degree days: <https://www.enova.no/kunnskap/graddagstall/>
:::

:::
:::

. . .

::: {.absolute top="%" left="0"}
::: {style="text-align: center"}

<!-- But are you really sure? -->
```{r, fig.width=4.5,fig.height=6}
library(tidyverse)
options(scipen=999)
# ---- make data from Enova ----
status <- c("Before retrofitting \n (2018)", "After retrofitting \n (2021)")
kwh <- c(800000, 500000)
df <- tibble(status,kwh)

status_before <- "Before retrofitting"
kwh_before <- 800000
df_before <- tibble(status_before,kwh_before)

ggplot(df, aes(x = reorder(status, -kwh), y = kwh)) +
  geom_col(width = 0.6, 
           fill="steelblue",
           position = position_dodge(0.1)) +
  theme_minimal() +
  geom_text(aes(label=format(kwh, big.mark = " ", scientific = FALSE)), vjust=1.6, color="white", size=4) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=16)) +
  xlab("") +
  ylab("Yearly energy consumption (kWh)") + 
  scale_y_continuous(labels=function(x) format(x, big.mark = " ", scientific = FALSE))

```

:::
:::


::: {.absolute top="28%" left="27%"}
::: {style="font-size: 0.5em"}

Corrected for </br>
temperature

:::
:::

## Documentation of energy savings

::: {.absolute top="0" left="100%"}
::: {.sectionhead}
[Objectives]{style="opacity:0.15"} </br> 
[Agenda]{style="opacity:0.15"} </br> 
[Background]{style="opacity:0.15"} </br> 
[Examples]{style="opacity:0.75"} </br> 
[Paper 1 / 5]{style="opacity:0.15"} </br> 
[Conclusion]{style="opacity:0.15"}  
:::
:::


::: {.absolute top="%" left="0"}
::: {style="text-align: center"}

```{r, fig.width=4.5,fig.height=6}
library(tidyverse)
options(scipen=999)
# ---- make data from Enova ----
status <- c("Before retrofitting \n (2018)", "After retrofitting \n (2021)")
kwh <- c(800000, 500000)
df <- tibble(status,kwh)

status_before <- "Before retrofitting"
kwh_before <- 800000
df_before <- tibble(status_before,kwh_before)

ggplot(df, aes(x = reorder(status, -kwh), y = kwh)) +
  geom_col(width = 0.6, 
           fill="steelblue",
           position = position_dodge(0.1)) +
  theme_minimal() +
  geom_text(aes(label=format(kwh, big.mark = " ", scientific = FALSE)), vjust=1.6, color="white", size=4) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=16)) +
  xlab("") +
  ylab("Yearly energy consumption (kWh)") + 
  scale_y_continuous(labels=function(x) format(x, big.mark = " ", scientific = FALSE))

```

:::
:::



::: {.absolute top="20%" left="45%"}
::: {style="font-size: 0.7em"}



You study the store in more detail...

::: {.incremental}
- Someone forgot the lights on during night
- Ventilation on during off-hours
- Error in the cooling system 
:::

:::
:::

::: {.absolute top="50%" left="45%"}
::: {style="font-size: 0.7em"}

::: {.fragment .fade-in}
It is not possible to change the weather :snowflake: </br>
:::

::: {.fragment .fade-in}
The other issues might have been fixed sooner
:::


:::
:::



## Documentation of energy savings

::: {.absolute top="0" left="100%"}
::: {.sectionhead}
[Objectives]{style="opacity:0.15"} </br> 
[Agenda]{style="opacity:0.15"} </br> 
[Background]{style="opacity:0.15"} </br> 
[Examples]{style="opacity:0.75"} </br> 
[Paper 1 / 5]{style="opacity:0.15"} </br> 
[Conclusion]{style="opacity:0.15"}  
:::
:::

::: {.absolute top="%" left="0"}
::: {style="text-align: center"}

```{r, fig.width=4.5,fig.height=6}
library(tidyverse)
options(scipen=999)
# ---- make data from Enova ----
status <- c("Before retrofitting \n (2018)", "After retrofitting \n (2021)")
kwh <- c(800000, 500000)
df <- tibble(status,kwh)

status_before <- "Before retrofitting"
kwh_before <- 800000
df_before <- tibble(status_before,kwh_before)

ggplot(df, aes(x = reorder(status, -kwh), y = kwh)) +
  geom_col(width = 0.6, 
           fill="steelblue",
           position = position_dodge(0.1)) +
  theme_minimal() +
  geom_text(aes(label=format(kwh, big.mark = " ", scientific = FALSE)), vjust=1.6, color="white", size=4) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=16)) +
  xlab("") +
  ylab("Yearly energy consumption (kWh)") + 
  scale_y_continuous(labels=function(x) format(x, big.mark = " ", scientific = FALSE))

```

:::
:::


::: {.absolute top="20%" left="45%"}
::: {style="font-size: 0.8em"}

Solution: </br>
a model to continuously monitor energy savings
 
:::
:::











